---
title: "Eating Out"
author: "Danitza Nunez"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "November 30,2022"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out.
Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  



```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
GSS <-read.dta(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

The data reflects that 80% of whites eat out the most. "Other" eat out about 78% percent of the time and the black race eat out 70% of the time. 


## Numerical Summary 
```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```


The numerical summary reflects that the whites eat out by 83%.   69% of Blacks eat out. "Other" eat out by about 78%. 

## FisherXY

```{r}
fisherXY(mydata$race,mydata$eatout)
```

The only races that were significant were "white" vs "Black", hence this was the only one that had a p value of less than 0.05.

Fisher's Exact Test

The whites are about 2.2 times more likely than to eat out than blacks. 

